---
title: "03-05 HW2 Solution"
author: "lhchien"
date: "2024-03-14"
output: github_document
---

#### *Consider the study of the effect of ploidy on the survival of patients with cancer of the tongue. Using the data on aneuploid tumors.*

#### *(a) Estimate the survival function. Use the KM estimator.*

讀入資料

```{r, warning=F}
#install.packages("KMsurv") #安裝套件
library(KMsurv)
data(tongue)
```

從中挑選出 aneuploid tumors 的病人

```{r}
tongue.1<-tongue[tongue$type==1,]
```
利用 *survfit* 指令得到 KM estimator

```{r}
library(survival)

r.km<-survfit(Surv(time,delta)~1,data=tongue.1)
summary(r.km)
```

根據 time 及 survival 欄位，可得到 survival function 的 KM estimator (S(t)) 為

```{r,echo=F}
r.t<-summary(r.km)$time #length(r.t)=27
r.t1<-c(0,r.t)
r.t2<-c(r.t,max(tongue.1$time))

t.range<-paste(r.t1,"<=t<",r.t2,sep="")
r.surv<-round(c(1,summary(r.km)$surv),digits=3)


r.table<-data.frame(1:length(t.range),t.range,r.surv)
colnames(r.table)<-c("index","time interval", "S(t)")
knitr::kable(r.table,align="cc")

```



#### *(b) plot the estimated survival curve.*

```{r}
plot(r.km, xlab = "Time to death(in weeks)",ylab = "Survival fuction")
```

#### *(c) Estimate the survival function at 12 weeks and 60 weeks after transplant. Find the standard errors for your estimates.*

```{r}
#S(12)
round(summary(r.km)$surv[sum(summary(r.km)$time<=12)],digits=3)
round(summary(r.km)$std.err[sum(summary(r.km)$time<=12)],digits=3)

#S(60)
round(summary(r.km)$surv[sum(summary(r.km)$time<=60)],digits=3)
round(summary(r.km)$std.err[sum(summary(r.km)$time<=60)],digits=3)

```
$\hat{S}(12) = 0.904$, standard error $se(\hat{S}(12)) = 0.041$  

$\hat{S}(60) = 0.654$, standard error $se(\hat{S}(60)) = 0.066$  




